Galaxy image statistical generator: how to be confident?

### 2024-09-10 paper/main.tex
experiemnt start

Concerning the training dataset, as we need to train two models with up to $100,000$ images each, we have used the SDSS (Sloan Digital Sky Survey) dataset ($306,006$ galaxies) used in \citep{smith2021}\footnoe{See \url{https://github.com/Smith42/astroddpm}} but first all images are cropped about the target coordinate galaxy to a shape of $64\times 64$ pixels and from the $z,g,r$ channels we produce a single  channel in gray levels in the range $[0,1]$ using \texttt{scipy} \citep{2020SciPy-NMeth} library\footnote{In particular the \texttt{make_lupton_rgb} function with $Q=8$ and $stretch=0.2$ setting}. Moreover the gray level is coded using 5-bits precision.
{\color{red}The training dataset is available in github}. In such scenario,  according to \cite{kadkhodaie2024generalization} results, the transition between memorization to generalisation regimes is expected using this dataset.

>>>>

Concerning the training dataset, as we need to train two models with up to $100,000$ images each, we have used the SDSS (Sloan Digital Sky Survey) dataset used in \citep{smith2021}\footnoe{See \url{https://github.com/Smith42/astroddpm} to obtain the raw data.} but first all images are cropped about the target coordinate galaxy to a shape of $64\times 64$ pixels and from the $z,g,r$ channels we produce a single  channel in gray levels in the range $[0,1]$ using \texttt{scipy} \citep{2020SciPy-NMeth} library\footnote{In particular the \texttt{make_lupton_rgb} function has been applied with $Q=8$ and $stretch=0.2$ setting}. Moreover, the gray level is coded using 5-bits precision.
{\color{red}The training dataset of $250,000$ galaxies is available in github}. With such dataset,  according to \cite{kadkhodaie2024generalization} results, the transition between memorization to generalisation regimes is expected to occur with size the range $10^4-10^5$.
